---
title: "RWorksheet_Gonzales#3b.R."
author: "Mamerto F. Gonzales Jr."
date: "`11/11/2022"
output: pdf_document
---

Worksheet-3b in R

Instructions:
• Use RStudio or the RStudio Cloud accomplish this worksheet.
• Save the R script as RWorksheet_lastname#3b.R.
• On your own GitHub repository, push the R script, the Rmd file, as well as this pdf worksheet to the repo you have created before.
• Do not forget to comment your Git repo on our VLE
• Accomplish this worksheet by answering the questions being asked and writing the code manually.

1. Create a data frame using the table below.

```{r}
Respondents <- c(1:20)
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
Fathers_Occupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
Persons_at_Home <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
Siblings_at_School <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
Types_of_Houses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
fam_data <- data.frame(Respondents, Sex, Fathers_Occupation, Persons_at_Home, Siblings_at_School, Types_of_Houses)
```

| a. Write the codes.
```{r}
fam_data
```
b. Describe the data. Get the structure or the summary of the data

```{r}
summary(fam_data)
```

c. Is the mean number of siblings attending is 5?

No, the mean number of siblings attending is 2.95.

d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.

```{r}
x1 <- subset(fam_data[1:2, 1:6, drop = FALSE])
x1
```

e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.

```{r}
x2 <- subset (fam_data[c(3, 5), c(2,4)])
x2
```
f. Select the variable types of houses then store the vector that results as types_houses.
Write the codes.

```{r}
types_houses <- subset(fam_data[c(6)])
types_houses
```
g. Select only all Males respondent that their father occupation was farmer. Write
the codes and its output.

```{r}
Males <- subset(fam_data[c(3,11),c(2,3)])
Males
```
h. Select only all females respondent that have greater than or equal to 5 number
of siblings attending school. Write the codes and its outputs.

```{r}
Females <- subset(fam_data[c(1,7, 13, 14, 18), c(2, 5)])
Females
```

2. Write a R program to create an empty data frame. Using the following codes:
df = data.frame(Ints=integer(),
Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))

```{R}
df = data.frame(Ints=integer(),
Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```

a. Describe the results.

The results of an empty data frame when printed is null. It also has either zero number of rows or zero number of columns. 

3. Interpret the graph.

The sentiments of Donald Trump's tweets per day are mostly negative.

Figure 1: Sentiments of Tweets per day - Donald Trump